---
title: "repData_peer1"
---



### Author: Matteo Forgiarini, Milan, Italy
Reading the data and checking file structure and lenght
```{r}
library(lattice)
setwd("~/Desktop/RepData_PeerAssessment1")
d=read.csv(file = "activity.csv")
head(d)
summary(d)
nrow(d)
```

Calculating the total number of steps taken per day
```{r}
attach(d)
a=data.frame(aggregate(steps~date, FUN=sum))
head(a)

```


Making a histogram of the total number of steps taken each day
```{r}
hist(a$steps, 10)

```
Calculating and reporting the mean and median of the total number of steps taken per day
```{r}
mean(a$steps)
median(a$steps)
```

Making a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r}
b=data.frame(aggregate(steps~interval, FUN=mean))
head(b)
detach(d)
attach(b)
plot(x = interval, y =steps, type = "l" )

```

Calculating the  5-minute interval, on average across all the days in the dataset, containing the maximum number of steps
```{r}
m=max(steps)
b[steps==m,]$interval

```

Calculating and reporting the total number of missing values in the dataset (i.e. the total number of rows with NAs)
```{r}
nrow(d) 
ok=complete.cases(d)
d1=d[!ok,]
nrow(d1)
head(d1, 10)

```
Devising a strategy for filling in all of the missing values in the dataset.

####I'm going to fill the Nas with the mean of their own interval averaged across the dataset.

Creating a new dataset that is equal to the original dataset but with the missing data filled in.
```{r}
b=data.frame(aggregate(d$steps~d$interval, FUN=mean))
head(b)
for(i in (1:nrow(d))) {
   d[i,1]= ifelse(is.na(d[i,1]), b[i,2], d[i,1])
}
head(d)
```
Making a histogram of the total number of steps taken each day and Calculating and reporting the mean and median total number of steps taken per day.
```{r}
head(d)
b=data.frame(aggregate(d$steps~d$date, FUN=sum))
head(b)
hist(b$d.steps,10)
mean(b$d.steps)
median(b$d.steps)
```
#### Mean and median total number of steps taken per day do not differ from estimates calculated before imputing Nas with data from specific interval.

Creating a new factor variable in the dataset with two levels  (weekday and weekend) indicating whether a given date is a weekday or weekend day.
```{r}
head(d)
d$daynumber=as.POSIXlt(d[[2]])$wday
head(d)
for(i in (1:nrow(d))) {
d[i,"daytype"]= ifelse((d[i,4]>0 & d[i,4]<6), "weekday", "weekend")
}
head(d)

```
Making a panel plot containing a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all weekday days or weekend days (y-axis).


```{r}
head(d)
wd=data.frame(aggregate(d[d$daytype=="weekday",]$steps~d[d$daytype=="weekday",]$interval, FUN=mean))
names(wd)=c("interval", "steps")
wd$daytype="weekday"
head(wd)

we=data.frame(aggregate(d[d$daytype=="weekend",]$steps~d[d$daytype=="weekend",]$interval, FUN=mean))
names(we)=c("interval", "steps")
we$daytype="weekend"
dd=rbind(wd,we)
xyplot  (steps ~ interval | daytype, data = dd,
type = "l", lty = 1)

```

```{r}

```